R for Clinical Study Reports and Submission

### 2021-10-14 slides/workshop-slides.Rmd

- Delivering TLFs in CSR (Yilong Zhang)
  + Session 1 (45 min)
  + Break (10 min)
  + Session 2 (45 min)
  + Break (20 min) 
- Clinical trial project (Nan Xiao)
  + Session 3 (40 min)
  + Break (10 min)
- eCTD submission package (Nan Xiao)
  + Session 4 (30 min)
  + Q&A (10 min)

>>>>

- Delivering TLFs in CSR (Yilong Zhang)
  + Session 1 (45 min)
  + Break (10 min)
  + Session 2 (45 min)
  + Break (20 min) 
- Clinical trial project (Nan Xiao)
  + Session 3 (30 min)
  + Break (10 min)
- eCTD submission package (Nan Xiao)
  + Session 4 (40 min)
  + Q&A (10 min)

### 2021-10-14 submission-environment.Rmd

::: {.rmdnote}
As of Q4 2021, the cleanslate package used in this chapter
is still under active development and validation.
This chapter gives a preview of the planned APIs.
They may change in the future.
:::

@@

- Create a project folder under `C:/temp/` with a `.Rproj` file;
- Download R 4.1.1 installer from CRAN, install it into `C:/temp/R/`;
- Not install Rtools (by default, `rtools_version = NULL`);
- Create a `.Rprofile` file under the project folder, set `options(repos)`
  to use the specified `repo` (an MRAN snapshot in this example),
  and instructions to set the R binary path in RStudio;
- Create a `.Renviron` file under the project folder and set the
  library path to be the library of the project-specific R installation.

@@

If using cleanslate, remember to update the ADRG instructions for
executing the analysis programs in R. Mostly, this would simplify
the first three steps on creating a project, installing a specific
version of R, and configuring the package repo location.

>>>>

::: {.rmdnote}
As of Q4 2021, the `cleanslate` package used in this chapter
is still under active development and validation.
This chapter gives a preview of the planned APIs.
They may change in the future.
:::

@@

- Create a project folder under `C:/temp/` with a `.Rproj` file;
- Download R `4.1.1` installer from CRAN, install it into `C:/temp/R/`;
- Not install Rtools (by default, `rtools_version = NULL`);
- Create a `.Rprofile` file under the project folder, set `options(repos)`
  to use the specified `repo` (an MRAN snapshot in this example),
  and instructions to set the R binary path in RStudio;
- Create a `.Renviron` file under the project folder and set the
  library path to be the library of the project-specific R installation.

@@

If using `cleanslate`, remember to update the ADRG instructions for
executing the analysis programs in R. Mostly, this would simplify
the first three steps on creating a project, installing a specific
version of R, and configuring the package repo location.

### 2021-10-14 tlf-ae-spec.Rmd

More discussion on `page_by`, `group_by`, and `subline_by` features can
be found in the [`r2rtf` package
website](https://merck.github.io/r2rtf/articles/example-sublineby-pageby-groupby.html).

>>>>

More discussion on `page_by`, `group_by` and `subline_by` 
features can be found in the 
[`r2rtf` package website](https://merck.github.io/r2rtf/articles/example-sublineby-pageby-groupby.html.

### 2021-10-14 tlf-ae-summary.Rmd

-   With one or more adverse events
-   With drug-related adverse events
-   With serious adverse events
-   With serious drug-related adverse events
-   Who "died"

>>>>

- With one or more adverse events
- With drug-related adverse events
- With serious adverse events
- With serious drug-related adverse events
- Who died"

### 2021-10-14 tlf-disposition.Rmd

In the code below, we calculate the number and percentage of participants who discontinued the study.

Here we use the `formatC()` function to customize the numeric value to be 1 decimal with fixed width of 5.

@@

In the final step, the individual rows are combined and used as input for `r2rtf.

>>>>

@@

Now we combined individual rows into the whole table for reporting purpose. 
`tbl_disp` is used as input for `r2rtf` to create final report.
